Synthesizing Quotient Lenses

### 2018-03-09 papers/QuotientLenses/main.tex
Fixed spacing weirdness in listings

\lstset{ language=Caml, basicstyle=\linespread{0.8}\upshape\sffamily,
keywordstyle=\upshape\sffamily\color{dkblue}, keepspaces=true,
framexleftmargin=1ex, framexrightmargin=1ex, showstringspaces=false,
keepspaces=true,
commentstyle=\itshape\rmfamily,
emph={synth,project,perm,squash,normalize,using,ins,del,lens},
emphstyle=\upshape\sffamily\color{dkblue}, columns=flexible,
% BCP: I find this distracting:
% stringstyle=\sffamily\color{dkred},
mathescape, }

@@

\begin{lstlisting}
let bib_to_end : (lens in bibtex $\Leftrightarrow$ endnote) =
synth bibtex $\Leftrightarrow$ endnote using {(bib_example, end_example)}
\end{lstlisting}
\bcp{Again, the spacing is weird}
\noindent Here, the generated  quotient lens synchronizes \cd{bibtex} and
\cd{endnote} formats, using \cd{bib_example} and \cd{end_example} (the two
concrete example strings given at the beginning of this section) to
disambiguate. In addition, and as we saw earlier with the definition of
\cd{s_to_c}, the synthesis procedure itself can be used to create lenses that
are in turn used to define other QREs.  The ability to intermix QRE
specification with QRE lens synthesis yields a powerful and flexible way of
creating bidirectional transformations.

>>>>

\lstset{ language=Caml, basicstyle=\linespread{0.8}\upshape\sffamily,
keywordstyle=\upshape\sffamily\color{dkblue}, keepspaces=true,
framexleftmargin=1ex, framexrightmargin=1ex, showstringspaces=false,
keepspaces=true,
commentstyle=\itshape\rmfamily,
emph={synth,project,perm,squash,normalize,using,ins,del,lens},
emphstyle=\upshape\sffamily\color{dkblue}, columns=fullflexible,
% BCP: I find this distracting:
% stringstyle=\sffamily\color{dkred},
mathescape, }

@@

\begin{lstlisting}
let bib_to_end : (lens in bibtex $\Leftrightarrow$ endnote) =
synth bibtex $\Leftrightarrow$ endnote using {(bib_example, end_example)}
\end{lstlisting}
\noindent Here, the generated  quotient lens synchronizes \cd{bibtex} and
\cd{endnote} formats, using \cd{bib_example} and \cd{end_example} (the two
concrete example strings given at the beginning of this section) to
disambiguate. In addition, and as we saw earlier with the definition of
\cd{s_to_c}, the synthesis procedure itself can be used to create lenses that
are in turn used to define other QREs.  The ability to intermix QRE
specification with QRE lens synthesis yields a powerful and flexible way of
creating bidirectional transformations.
